Assignment 3

### 2015-02-16 rmtw/a3/latex8.tex
Draft of Validity threats and new introduction

\SubSection{Problem Statement}
%big problem in industry implementing change
%could a reason for this be because they're trying to fit one thing onto something different. Focus on implementation rather than what the changes are

@@

\Section{Threats to Validity}
%getting too close, potential bias
%change manager bias, if they implemented
%generalisability

%Check text for more.
%% Talk about generalisability tomorrow with willski

%gatekeeper to help sample, he could, in some way, select persons that are positive. We give up control to the judgement of the gatekeeper

%only doing it at EPG.
%doing it at different times, only one company -> generalise

>>>>

Paradigms in this context will be considered to be those which relate to software development. For example, we would consider Model Driven Software Development[CITE] to be a paradigm. Specifically, in this situation with our partner company, we use the term manual coding to mean development without the use of any particular paradigm. The difference being that MDSD is heavily focused upon models and a high level of abstraction for the design of code, whereas manual coding is a standard development process. Other examples of change could be seen as a company wishing to implement processes such as Scrum or introducing Test Driven Development.

\SubSection{Problem Statement}
Change is always a challenge in industry and one that is not going away anytime soon. This is especially true when it comes to changing development processes or paradigms. One possible reason that these changes are far more difficult than others could be because the companies introducing these changes overlook the possibility that the changes they wish to implement are at odds with their current development paradigms or processes. This is the problem that this paper will attempt to address; how industry can determine what changes are suitable to implement taking into consideration their existing paradigms?

@@

\Section{Threats to Validity}

While designing the study, validity concerns were taken into consideration. The most pressing of which would be the limited scope of the study. The fact that the study only occurred in a subset of Ericsson and not a larger part of the company means that we cannot reliably make any generalities about the results. This is something that could be overcome during a potential triangulation period. For example, further studies could be conducted within Ericsson at other departments which could then be used to strengthen or diminish the results from this study.

Other validity issues concern bias. The potential for bias lies with both the subjects and researchers of the study [maybe cite?]. There is a risk that we, the researches, can be drawn too close to the company and as such might overlook or miss certain results that would otherwise be obvious to someone not so intimately involved. The potential for this bias is greater considering one of the researchers has previously held employment in the EPG department where the study took place. This potential for bias extends further to the respondents of the interviews. The respondents might have been intimidated by the interview procedure and potentially for repercussions to their positions within the company based on their answers to the questions. This is entirely possible despite the assurance that the responses would be anonymous. Finally, the gatekeeper is also a potential point of bias. In this study, the gatekeeper assisted with the sampling of potential interview candidates, while unlikely, there is potential that the gatekeeper could have selected individuals whom would have a favourable opinion about the material that the interview questions were concerned with.
